RUPEE: A fast and accurate purely geometric protein structure search

### 2019-01-10 docs/rupee_2.tex
lcs explanation

In fast mode, the top 8,000 matches from the min-hashing and LSH initial filtering are obtained along with the original gram sequences defined for the structures.
A further validation is done by performing a longest common subsequence (LCS) analysis of the matched gram sequences and adjusting the Jaccard similarity scores accordingly.
This step accounts for possible gram matches among pairs of structures that are out of order since the min-hashing and LSH techniques themselves do not consider the order of the gram matches.
The final step of fast mode is to sort the matches based on the adjusted scores and return the results.

>>>>

In fast mode, the top 8,000 matches from the min-hashing and LSH initial filtering are obtained.
For each match, we calculate the exact denominator in the definition of Jaccard similarity from the original shingle sequences of the structures.
As for the numerator, instead of using the total number of matched shingles, we use the length of the longest common subsequence (LCS) of the shingle sequences for each match. 
This LCS adjustment to the Jaccard similarity enforces the constraint that all valid shingles matches must appear in order along the length of each structure. 
The final step of fast mode is to sort the matches based on the adjusted scores and return the results.
